On the Minimum Core Mass for Giant Planet Formation at Wide Separations

### 2013-10-25 tex/draft/draft4.tex
added ackowledgements
very minor typos in section 4

\subsection{Atmospheric Stucture}
\label{sec:profiles}
Figure \ref{fig:profiles} shows radial profiles at different stages of atmospheric growth around $5 M_{\oplus}$ core at $60$ AU.  Quoted mass values include the core plus atmosphere within the smaller of $\RB$ or $\RH$, which for these cases is $\RB$.  The 9.24 $M_{\oplus}$ solution is the highest mass we can reach in our evolutionary sequence, as we explain further in \S\ref{sec:endoftime}.

@@

We examine the  validity of our cooling model by compare our model luminosity to the neglected luminosity, $L_{\rm negl}$,  that a more detailed model would generate in the radiative zone.  We compute $L_{\rm negl}$ from the entropy difference between successive radiative zone solutions.  We then integrate the energy equation, $\p L / \p m = - T \p S/ \p t$, over the average depth of the radiative zone.\footnote{While useful as a diagnostic, the neglected luminosity cannot reliably correct the global cooling model because the effects of $L_{\rm negl}$ on the structure of the radiative zone are still ignored.}

 \Fig{fig:coolingterms} shows that the neglected luminosity is indeed negligible during the early stages of evolution.  However, $L_{\rm negl}$ exceeds the model luminosity, $L$, at high masses, $M_{\rm atm} > 3 M_\oplus$ in this case.  Our cooling model is thus inaccurate at higher masses.  However the model remains reasonably accurate up to the beginning stages of runaway growth, which is sufficient for our purposes of widely exploring parameter space and exploring trends.

@@

At even higher masses than shown in \Fig{fig:coolingterms}, our cooling model breaks down.  Mathematically, the breakdown manifests as negative time step (due to an increase in internal entropy) when advancing to a higher atmospheric mass.  This unphysical result has no deep significance, as the neglected luminosity overwhelms the model luminosity by this point.    Effectively the model is telling us when to ignore it.  Our results are unaffected by the breakdown, which occurs comfortably after $t_{\rm run}$, our threshold for runaway growth.

@@

>>>>

\subsection{Atmospheric Stucture}
\label{sec:profiles}
Figure \ref{fig:profiles} shows radial profiles at different stages of atmospheric growth around a $5 M_{\oplus}$ core at $60$ AU.  Quoted mass values include the core plus atmosphere within the smaller of $\RB$ or $\RH$, which for these cases is $\RB$.  The 9.24 $M_{\oplus}$ solution is the highest mass we can reach in our evolutionary sequence, as we explain further in \S\ref{sec:endoftime}.

@@

We examine the  validity of our cooling model by comparing our model luminosity to the neglected luminosity, $L_{\rm negl}$,  that a more detailed model would generate in the radiative zone.  We compute $L_{\rm negl}$ from the entropy difference between successive radiative zone solutions.  We then integrate the energy equation, $\p L / \p m = - T \p S/ \p t$, over the average depth of the radiative zone.\footnote{While useful as a diagnostic, the neglected luminosity cannot reliably correct the global cooling model because the effects of $L_{\rm negl}$ on the structure of the radiative zone are still ignored.}

 \Fig{fig:coolingterms} shows that the neglected luminosity is indeed negligible during the early stages of evolution.  However, $L_{\rm negl}$ exceeds the model luminosity, $L$, at high masses, $M_{\rm atm} > 3 M_\oplus$ in this case.  Our cooling model is thus inaccurate at higher masses.  However, the model remains reasonably accurate up to the beginning stages of runaway growth, which is sufficient for our purposes of widely exploring parameter space and exploring trends.

@@

At even higher masses than shown in \Fig{fig:coolingterms}, our cooling model breaks down.  Mathematically, the breakdown manifests as a negative time step (due to an increase in internal entropy) when advancing to a higher atmospheric mass.  This unphysical result has no deep significance, as the neglected luminosity overwhelms the model luminosity by this point.    Effectively the model is telling us when to ignore it.  Our results are unaffected by the breakdown, which occurs comfortably after $t_{\rm run}$, our threshold for runaway growth.

@@

\acknowledgements{We thank Ruth Murray-Clay for detailed feedback and skillful proof reading. We also thank Eugene Chiang for a valuable conversation.}
